Online Laterality Battery Pre-Processing - short version

### 2020-07-06 battery-preprocessing_v5_DB.Rmd
smallest number of trials for good test-retest

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#NB for original data setwd("~/Dropbox/Online LDT/300 Ps")
# libraries 
library(readr)
library(yarrr)
library(dplyr)
library(tidyr)
library(car)
library(ggplot2)
library(knitr)
require(readr)  # for read_csv()
require(dplyr)  # for mutate()
require(purrr)  # for map(), reduce()
library(GGally)
require(stringr) # string matching
library(ggpirate)
library(corrr) #easier correlations!
library(beeswarm) #just a kind of plot Dorothy likes
```

@@

```{r demograhics, warning=FALSE}
#Reading from OSF - this only works if files are public

demo_dat <- read.csv('./data/Demographics.csv',stringsAsFactor=F)

@@

allsum$genderpch <-2
w<-which(allsum$gender=='Male')
allsum$genderpch[w] <-1
w<-which(allsum$gender=='Prefer not to say')
allsum$genderpch[w]<-NA

@@

```{r sightednesss, warning=FALSE}
porta_dat <- read.csv("./data/Porta.csv",stringsAsFactors = F)
miles_dat <-  read.csv("./data/Miles.csv",stringsAsFactors = F)

@@

```{r EHI, warning=FALSE}

EHI <- read.csv("./data/EHI.csv",stringsAsFactors = F)

@@

```{r lexTALE, warning=FALSE}
# read data
lexTALE <- read.csv("./data/LexTALE.csv",stringsAsFactors = F)

@@

# remove those who dIDn't pass the LexTALE
allsum <- allsum[allsum$lexTALE >= 80,]
```

@@

```{r readraw,include= FALSE, warning=FALSE}
# Set directory
for (d in 1:2){
  data_file <- "./data/combined/day1_combined.csv" #day 1 data

  if (d ==2){
    data_file <-  "./data/combined/day2_combined.csv"
  }
  #we will assign raw data to all_dat2 (day2), but then reassign to all_dat1 on first run through loop, so we have correct data for each day
all_dat2 <- read.csv(data_file, na.strings = "NA",stringsAsFactors=F)
# cleaning - do operations that apply for all tasks
all_dat2 %>% filter(Attempt >= 1) # only answers 
# write as factors
all_dat2$subject <- as.factor(all_dat2$Participant.Public.ID)
all_dat2$RT <- as.numeric(as.character(all_dat2$Reaction.Time))
all_dat2$Trial <-as.numeric(all_dat2$Trial.Number) #useful if we want to restrict analysis to subset of trials so retain this variable
all_dat2$Task.Name <- as.factor(all_dat2$Task.Name)
all_dat2$word<-substring(all_dat2$word,66,(nchar(all_dat2$word)-4)) #remove format from written word stimuli
if (d==1)
{all_dat1 <- all_dat2}
}

@@

CF_same2 <- CF_dat_all[CF_dat_all$l_hemiface == CF_dat_all$r_hemiface,] # create data frame for non-chimeras
CF_dat2 <- CF_dat_all[CF_dat_all$l_hemiface != CF_dat_all$r_hemiface,] # create df for chimeras: remove items where same expression in both hemifaces
if (d==1)
{CF_dat1 <- CF_dat2
 CF_same1 <- CF_same2}
}
```

@@

```{r CFoutliers}
CF_dat1 <- detect.outliers(CF_dat1,200,1.65) #use generic outlier detection function. The parameters are lowcut (200 ms cutoff for anticipations) and then the value used for Hoaglin Iglewicz (1.65)
outliertable1<-table(CF_dat1$subject,CF_dat1$outlier)
CF_dat2 <- detect.outliers(CF_dat2,200,1.65) #use generic outlier detection function. The parameters are lowcut (200 ms cutoff for anticipations) and then the value used for Hoaglin Iglewicz (1.65)
outliertable2<-table(CF_dat2$subject,CF_dat2$outlier)
#Most have 96 accepted trials in CF_dat2. A few have 1-2 - these seem to be ones that had RTs < 200, and may have been responding rapidly at random.

@@

  # removed code to compute correct, as already done above
  # calculate participants average
  #update: do this for chimeric as well as Same trials
  emot_corr_Same <- aggregate(FUN= mean, data= CF_same, Correct~ subject)
  # add this to allsum 
  colnames(emot_corr_Same)[2]<-'Emot_corr_same'
  allsum <- merge(allsum, emot_corr_Same, by= "subject")
  emot_corr_Diff <- aggregate(FUN= mean, data= CF_diff, Correct~ subject)
  # add this to allsum 
  colnames(emot_corr_Diff)[2]<-'Emot_corr_diff'
  allsum <- merge(allsum, emot_corr_Diff, by= "subject",all.x=T)
}

@@

```{r CFhanded}

t.test(allsum$Day1_CF_acc_Z~allsum$handpch)
t.test(allsum$Day2_CF_acc_Z~allsum$handpch)
beeswarm(Day1_CF_acc_Z~handedness, data = allsum, 
  pch = 16, cex=.5,col = rainbow(8),
  main = 'Day 1')
beeswarm(Day2_CF_acc_Z~handedness, data = allsum, 
  pch = 16, cex=.5,col = rainbow(8),
  main = 'Day 2')
```
## Next Question: Does CF laterality relate to task accuracy
Just looks at correlations and plot scattergram.

@@

dichotic_same2 <- dichotic_all[dichotic_all$left_channel == dichotic_all$right_channel,] # create data frame for trials with both ears same
dichotic_dat2 <- dichotic_all[dichotic_all$left_channel != dichotic_all$right_channel,] # remove items where same expression in both hemifaces
if (d==1)
{dichotic_dat1 <- dichotic_dat2
 dichotic_same1 <- dichotic_same2}
}
```

Now remove outliers, using same function as for CF.
```{r dichotic.outliers}
dichotic_dat1 <- detect.outliers(dichotic_dat1,200,1.65) #use generic outlier removal function
outliertable1<-table(dichotic_dat1$subject,dichotic_dat1$outlier)
dichotic_dat2 <- detect.outliers(dichotic_dat2,200,1.65) #use generic outlier removal function
outliertable2<-table(dichotic_dat2$subject,dichotic_dat2$outlier)
#print(outliertable)

```
Inspection of outliertable1 and outliertable2 shows most are data as expected, with 120 trials. Outliers not v numerous. Occasional cases where test does not seem to be done, just one trial recorded.

@@

  allsum <- merge(allsum, sound_mean, by= "subject",all.x=T)
  allsum <- merge(allsum, dichotic_acc, by= "subject",all.x=T)
}

@@

```{r Cdichotic_acc}
cor1 <- round(cor(partsum$Day1_Dich_acc_Z,partsum$dichotic.acc1,use="complete.obs"),3)
plot(partsum$Day1_Dich_acc_Z,partsum$dichotic.acc1)
text(15,.6,paste0('r = ',cor1))
cor2 <- round(cor(partsum$Day2_Dich_acc_Z,partsum$dichotic.acc2,use="complete.obs"),3)
plot(partsum$Day2_Dich_acc_Z,partsum$dichotic.acc2)
text(15,.6,paste0('r = ',cor2))

@@

  # count subjects
nsub <-length(unique(RDT_dat2$subject))
print(paste0("Day ",d," subjects: ", nsub))
if(d==1)
  {RDT_dat1 <- RDT_dat2}
}
```
Now use generic function to remove outliers.

@@

# add log RT
RDT_df1$logRT <- log10(RDT_df1$RT)
RDT_df2$logRT <- log10(RDT_df2$RT)

@@

# RT
origdat$X1 <- origdat$RT
measure <- 'RT'
dopirate(origdat,task,measure)

# log RT
origdat$X1 <- origdat$logRT
measure <- 'logRT'
dopirate(origdat,task,measure)
}
```

@@

# RT
origdat$X1 <- origdat$RT
mycolname<-"Day1.RDT_RT_LI"
if(d==2){mycolname<-"Day2.RDT_RT_LI"}
polarity <- (-1)
allsum <- makeLI(allsum,origdat,task,mycolname,polarity,mycutoff)

# log-RT
origdat$X1 <- origdat$logRT
mycolname<-"Day1.RDT_logRT_LI"
if(d==2){mycolname<-"Day2.RDT_logRT_LI"}
polarity <- (-1)
mycutoff <- 0
allsum <- makeLI(allsum,origdat,task,mycolname,polarity,mycutoff)
}

#t.test to test if laterality index differs from zero
partsum <- allsum[allsum$exRDT==0,]
print('Testing for difference of single mean from zero')
t.test(partsum$Day1.RDT_p.corr_LI)
t.test(partsum$Day1.RDT_RT_LI)
t.test(partsum$Day1.RDT_logRT_LI)
t.test(partsum$Day2.RDT_p.corr_LI)
t.test(partsum$Day2.RDT_RT_LI)
t.test(partsum$Day2.RDT_logRT_LI)

# correlate
cor1<-cor(partsum$Day1.RDT_p.corr_LI,partsum$Day2.RDT_p.corr_LI,use='complete.obs')
cor2<-cor(partsum$Day1.RDT_RT_LI,partsum$Day2.RDT_RT_LI,use='complete.obs')
cor3<-cor(partsum$Day1.RDT_logRT_LI,partsum$Day2.RDT_logRT_LI,use='complete.obs')
# acc plot
plot(partsum$Day1.RDT_p.corr_LI,partsum$Day2.RDT_p.corr_LI,main='Rhyme detect: LI for accuracy (%correct)')
abline(v=0)
abline(h=0)
text(-3,3,paste0('r = ',round(cor1,3)))
# raw plot
plot(partsum$Day1.RDT_RT_LI,partsum$Day2.RDT_RT_LI,main='Rhyme detect: LI for RT')
abline(v=0)
abline(h=0)
text(-3,9,paste0('r = ',round(cor2,3)))
# log plot
plot(partsum$Day1.RDT_logRT_LI,partsum$Day2.RDT_logRT_LI,main='Rhyme detect: LI for log-RT')
abline(v=0)
abline(h=0)
text(2,1,paste0('r = ',round(cor3,3)))
```
## Does RDT relate to handedness?
Answer is convincing nope!

@@

@@

if(d==1){all_finger1 <- finger}
}
```

@@

## Final sample summary

Here we report the descriptives for the participants who had full datasets. 
(Some of these tests etc have been incorporated in analyses above, so can be pruned from script)

```{r Finalallsum, warning=FALSE}
# first, describe age for the whole sample and plot
allsum %>%
    summarize(avg = mean(age), n = n(), sd = sd(age))
# second, show gender count for the whole population
allsum %>%
  group_by(gender) %>%
    summarize(n = n())
# third, show footedness
allsum %>%
  group_by(footedness) %>%
    summarize(n = n())
# fourth, show handedness
allsum %>%
  group_by(handedness) %>%
    summarize(n = n())
# fifth, show bilingualism
allsum %>%
  group_by(bilingual) %>%
    summarize(n = n())
# sixth, show miles
allsum %>%
  group_by(miles) %>%
    summarize(n = n())
# seventh, show porta
allsum %>%
  group_by(porta) %>%
    summarize(n = n())
# eigth, show LexTALE
allsum %>%
    summarize(avg = mean(lexTALE), n = n(), sd = sd(lexTALE))
```

```{r finalplots}
# Now that we have the basic scores, let's look at how this looks with regards to handedness
# first, describe age for the whole sample and plot
plot(data=allsum, index_EHI ~ age,col=handpch,xlim=c(18,50),pch=(14+allsum$genderpch))

allsum$handfac <- as.factor(allsum$handedness)
allsum$genderfac <- as.factor(allsum$genderpch)
levels(allsum$genderfac)<-c('male','female')

a <- allsum %>%
  group_by(genderfac, handfac) %>%
    summarize(n = n())

ggplot(data=a, aes(x=handfac, y=n, fill= handfac)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=n), vjust=1.6, color="white", size=3.5)+
  theme_classic() + facet_wrap(.~ genderfac) + ggtitle("Gender by handedness") +   ylab("Count") + xlab("")

# third, show footedness
a <- allsum %>%
  group_by(handfac, footedness) %>%
    summarize(n = n())
ggplot(data=a, aes(x=handfac, y=n, fill= handfac)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=n), vjust=1.6, color="white", size=3.5)+
  theme_classic() + facet_wrap(.~ footedness) + ggtitle("Footedness by handedness") + 
  ylab("Count") + xlab("")

# fourth, show bilingualism
a <- allsum %>%
  group_by(bilingual,handfac) %>%
    summarize(n = n())

# fifth, show miles
a <- allsum %>%
  group_by(miles, handfac) %>%
    summarize(n = n())
ggplot(data=a, aes(x=handfac, y=n, fill= handfac)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=n), vjust=1.6, color="white", size=3.5)+
  theme_classic() + facet_wrap(.~ miles) + ggtitle("Mile test by handedness") + 
  ylab("Count") + xlab("")
# six, show porta
a <- allsum %>%
  group_by(porta, handfac) %>%
    summarize(n = n())
ggplot(data=a, aes(x=handfac, y=n, fill= handfac)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=n), vjust=1.6, color="white", size=3.5)+
  theme_classic() + facet_wrap(.~ porta) + ggtitle("Porta test by handedness") + 
  ylab("Count") + xlab("")
# seventh, show LexTALE
ggplot(allsum, aes(x = handfac, y = lexTALE)) +
  geom_pirate(aes(colour = handfac), bars = FALSE) + theme_classic() + 
  ylim(70, 110) + ggtitle("LexTALE by handedness") + ylab("Standardised score") + xlab("")
```

```{r corr_between_tasks}
mycols <- c('Day1_CF_acc_Z','Day2_CF_acc_Z','Day1_Dich_acc_Z','Day2_Dich_acc_Z','Day1_Finger_acc_Z','Day2_Finger_acc_Z')
colnums<- which(colnames(allsum) %in% mycols)
mycorrs<-correlate(allsum[,colnums],method='spearman')

mycorrsL <-correlate(allsum[allsum$handedness=='Left',colnums],method='spearman')
mycorrsR <-correlate(allsum[allsum$handedness=='Right',colnums],method='spearman')

#compare L and R handers

for (i in colnums){
  print(names(allsum)[i])
 print(t.test(allsum[,i]~allsum$handedness))
}

#check lateralisation with single group t vs zero
for (i in colnums){
  print(names(allsum)[i])
 print(t.test(allsum[,i]))
}

>>>>

1st July 2020: AP edits
(1) no longer remove lexTALE in file. I think this will make things a little easier when descirbing missing data in the MS.
(2) corrected the issue wrong files being marked for removal where accuracy is less than 75% (comma in the wrong place).
(3) identifiers for participants who completed both days
(4) save data frames to plot average performance across tasks in MS.
(5) Now include minimum number of trials to achieve .75 ttest-retest.

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# libraries 
library(readr)
library(yarrr)
library(dplyr)
library(tidyr)
library(car)
library(ggplot2)
library(knitr)
require(readr)  # for read_csv()
require(dplyr)  # for mutate()
require(purrr)  # for map(), reduce()
library(GGally)
require(stringr) # string matching
library(ggpirate)
library(corrr) #easier correlations!
library(beeswarm) #just a kind of plot Dorothy likes
```

@@

```{r demograhics, warning=FALSE}
#Reading from OSF - this only works if files are public
demo_dat <- read.csv('https://osf.io/7smj6/download',stringsAsFactors = F)

@@

allsum$genderpch <-2
w<-which(allsum$gender=='Male')
allsum$genderpch[w] <-1
w<-which(allsum$gender=='Prefer not to say')
allsum$genderpch[w]<-NA
```

@@

```{r sightednesss, warning=FALSE}
porta_dat <- read.csv("https://osf.io/zmqkt/download",stringsAsFactors = F)
miles_dat <-  read.csv("https://osf.io/ekqsp/download",stringsAsFactors = F)

@@

```{r EHI, warning=FALSE}
EHI <- read.csv("https://osf.io/kfdma/download",stringsAsFactors = F)

@@

```{r lexTALE, warning=FALSE}
# read data
lexTALE <- read.csv("https://osf.io/h4btp/download",stringsAsFactors = F)

@@

# mark those who ID don't pass the LexTALE
allsum <- allsum %>% mutate(lexOut= if_else(lexTALE < 80, "remove", "keep"))
```

@@

```{r readraw,include= FALSE, warning=FALSE}
# Set directory
for (d in 1:2){
  data_file <- "https://osf.io/mhk29/download" #day 1 data

  if (d ==2){
    data_file <-  "https://osf.io/ebm6s/download"
  }
  #we will assign raw data to all_dat2 (day2), but then reassign to all_dat1 on first run through loop, so we have correct data for each day
all_dat2 <- read.csv(data_file, na.strings = "NA",stringsAsFactors=F)
# cleaning - do operations that apply for all tasks
all_dat2 %>% filter(Attempt >= 1) # only answers 
# write as factors
all_dat2$subject <- as.factor(all_dat2$Participant.Public.ID)
all_dat2$RT <- as.numeric(as.character(all_dat2$Reaction.Time))
all_dat2$Trial <-as.numeric(all_dat2$Trial.Number) #useful if we want to restrict analysis to subset of trials so retain this variable
all_dat2$Task.Name <- as.factor(all_dat2$Task.Name)
all_dat2$word<-substring(all_dat2$word,66,(nchar(all_dat2$word)-4)) #remove format from written word stimuli
if (d==1)
{all_dat1 <- all_dat2}
}

@@

CF_same2 <- CF_dat_all[CF_dat_all$l_hemiface == CF_dat_all$r_hemiface,] # create data frame for non-chimeras
CF_dat2 <- CF_dat_all[CF_dat_all$l_hemiface != CF_dat_all$r_hemiface,] # create df for chimeras: remove items where same expression in both hemifaces
if (d==1)
{CF_dat1 <- CF_dat2
 CF_same1 <- CF_same2}
}

# lets keep a running check on the participants completing here
complete.day2.CF <- unique(CF_dat2$subject)
```

@@

```{r CFoutliers}
CF_dat1 <- detect.outliers(CF_dat1,200,1.65) #use generic outlier detection function. The parameters are lowcut (200 ms cutoff for anticipations) and then the value used for Hoaglin Iglewicz (1.65)
outliertable1<-table(CF_dat1$subject,CF_dat1$outlier)
CF_dat2 <- detect.outliers(CF_dat2,200,1.65) #use generic outlier detection function. The parameters are lowcut (200 ms cutoff for anticipations) and then the value used for Hoaglin Iglewicz (1.65)
outliertable2<-table(CF_dat2$subject,CF_dat2$outlier)
#Most have 96 accepted trials in CF_dat2. A few have 1-2 - these seem to be ones that had RTs < 200, and may have been responding rapidly at random.
```

@@

  # removed code to compute correct, as already done above
  # calculate participants average
  #update: do this for chimeric as well as Same trials
  emot_corr_Same <- aggregate(FUN= mean, data= CF_same, Correct~ subject)
  # add this to allsum 
  colnames(emot_corr_Same)[2]<-'Emot_corr_same'
  allsum <- merge(allsum, emot_corr_Same, by= "subject", all = TRUE)
  emot_corr_Diff <- aggregate(FUN= mean, data= CF_diff, Correct~ subject)
  # add this to allsum 
  colnames(emot_corr_Diff)[2]<-'Emot_corr_diff'
  allsum <- merge(allsum, emot_corr_Diff, by= "subject",all=TRUE)
}

@@

```{r CFhanded}
t.test(allsum$Day1_CF_acc_Z~allsum$handpch)
t.test(allsum$Day2_CF_acc_Z~allsum$handpch)
beeswarm(Day1_CF_acc_Z~handedness, data = allsum, 
  pch = 16, cex=.5,col = rainbow(8),
  main = 'Day 1')
beeswarm(Day2_CF_acc_Z~handedness, data = allsum, 
  pch = 16, cex=.5,col = rainbow(8),
  main = 'Day 2')
```

## Next Question: Does CF laterality relate to task accuracy
Just looks at correlations and plot scattergram.

@@

dichotic_same2 <- dichotic_all[dichotic_all$left_channel == dichotic_all$right_channel,] # create data frame for trials with both ears same
dichotic_dat2 <- dichotic_all[dichotic_all$left_channel != dichotic_all$right_channel,] # remove items where same expression in both hemifaces
if (d==1)
{dichotic_dat1 <- dichotic_dat2
 dichotic_same1 <- dichotic_same2}
}

# lets keep a running check on the participants completing here
complete.day2.DL <- unique(dichotic_dat2$subject)
```

Now remove outliers, using same function as for CF.
```{r dichotic.outliers}
dichotic_dat1 <- detect.outliers(dichotic_dat1,200,1.65) #use generic outlier removal function
outliertable1<-table(dichotic_dat1$subject,dichotic_dat1$outlier)
dichotic_dat2 <- detect.outliers(dichotic_dat2,200,1.65) #use generic outlier removal function
outliertable2<-table(dichotic_dat2$subject,dichotic_dat2$outlier)
#print(outliertable)
```

Inspection of outliertable1 and outliertable2 shows most are data as expected, with 120 trials. Outliers not v numerous. Occasional cases where test does not seem to be done, just one trial recorded.

@@

  allsum <- merge(allsum, sound_mean, by= "subject",all=TRUE)
  allsum <- merge(allsum, dichotic_acc, by= "subject",all.x=TRUE)
}

@@

```{r Cdichotic_acc}
cor1 <- round(cor(partsum$Day1_Dich_acc_Z,partsum$dichotic.acc1,use="complete.obs"),3)
plot(partsum$Day1_Dich_acc_Z,partsum$dichotic.acc1)
text(15,.6,paste0('r = ',cor1))
cor2 <- round(cor(partsum$Day2_Dich_acc_Z,partsum$dichotic.acc2,use="complete.obs"),3)
plot(partsum$Day2_Dich_acc_Z,partsum$dichotic.acc2)
text(15,.6,paste0('r = ',cor2))
```

@@

  # count subjects
nsub <-length(unique(RDT_dat2$subject))
print(paste0("Day ",d," subjects: ", nsub))
if(d==1)
  {RDT_dat1 <- RDT_dat2}
}

# lets keep a running check on the participants completing here
complete.day2.RD <- unique(RDT_dat2$subject)
```

Now use generic function to remove outliers.

@@

@@

# RT
origdat$X1 <- origdat$RT
measure <- 'RT'
dopirate(origdat,task,measure)
}
```

@@

# RT
origdat$X1 <- origdat$RT
mycolname<-"Day1.RDT_RT_LI"
if(d==2){mycolname<-"Day2.RDT_RT_LI"}
polarity <- (1)
allsum <- makeLI(allsum,origdat,task,mycolname,polarity,mycutoff)
}

#t.test to test if laterality index differs from zero
partsum <- allsum[allsum$exRDT==0,]
print('Testing for difference of single mean from zero')
t.test(partsum$Day1.RDT_p.corr_LI)
t.test(partsum$Day1.RDT_RT_LI)
t.test(partsum$Day2.RDT_p.corr_LI)
t.test(partsum$Day2.RDT_RT_LI)

# correlate
cor1<-cor(partsum$Day1.RDT_p.corr_LI,partsum$Day2.RDT_p.corr_LI,use='complete.obs')
cor2<-cor(partsum$Day1.RDT_RT_LI,partsum$Day2.RDT_RT_LI,use='complete.obs')
# acc plot
plot(partsum$Day1.RDT_p.corr_LI,partsum$Day2.RDT_p.corr_LI,main='Rhyme detect: LI for accuracy (%correct)')
abline(v=0)
abline(h=0)
text(-3,3,paste0('r = ',round(cor1,3)))
# raw plot
plot(partsum$Day1.RDT_RT_LI,partsum$Day2.RDT_RT_LI,main='Rhyme detect: LI for RT')
abline(v=0)
abline(h=0)
text(-3,9,paste0('r = ',round(cor2,3)))
```
## Does RDT relate to handedness?
Answer is convincing nope!

@@

### log RT

In our pre-reg, we also specified that we would use logRT. So we add this in here.

```{r logRT analysis}
# now add the logRT to original output
# first relabel df
RDT_logdat1 <- RDT_dat1
RDT_logdat2 <- RDT_dat2
# now log the RT
RDT_logdat1$RT <- log(RDT_dat1$RT)
RDT_logdat2$RT <- log(RDT_dat2$RT)
# Now use generic function to remove outliers.
# Here we keep the 1.65 of the H&I removal. 
# BUT we now specify log 200 for lower cutoff to move onto the same scale
RDT_logdat1<-detect.outliers(RDT_logdat1,log(200),1.65) #numbers specify min RT and 
RDT_logdat2<-detect.outliers(RDT_logdat2,log(200),1.65) #numbers specify min RT and zscore for Hoaglin-Iglewicz respectiv
# We create logRT for day1 and day 2
varlist <-   c("subject", "side", "accurate", "RT") #need to be in this order, ie sub, side, acc and RR
latlist <- c("left","no rhyme","right") #names of factor levels
nloop<-length(latlist)
RDT_log_df1 <- make.df(RDT_logdat1,varlist,latlist,nloop)
RDT_log_df2 <- make.df(RDT_logdat2,varlist,latlist,nloop)
# remove NaN
is.nan.data.frame <- function(x)
  do.call(cbind, lapply(x, is.nan))
RDT_log_df1[is.nan(RDT_log_df1)] <- NA
RDT_log_df2[is.nan(RDT_log_df2)] <- NA
# now let's plot the log data
for (d in 1:2){
origdat <-RDT_log_df1[RDT_log_df1$subject %in% incRDT,]
if (d==2)
{origdat <-RDT_log_df2[RDT_log_df2$subject %in% incRDT,]}
origdat <-origdat[origdat$side %in% c('left','right'),]
# RT
origdat$X1 <- origdat$RT
measure <- 'log-RT'
dopirate(origdat,task,measure)
}
# make LI for log RT
# Because outliers will already be marked in allsum, we won't bother going through this again. 
# We will intead add straight into the data frame. 
#now create LI
for (d in 1:2){
origdat <-RDT_log_df1[RDT_log_df1$subject %in% incRDT,]
if (d==2)
{origdat <-RDT_log_df2[RDT_log_df2$subject %in% incRDT,]}
# log RT
origdat$side <- as.factor(origdat$side)
  levels(origdat$side) <-c('Left','No rhyme','Right') #function assumes capitalised
polarity<- 1 #so LI is positive in predicted direction
mycutoff <- 0
origdat$X1 <- origdat$RT
mycolname<-"Day1_RDT_logRT_LI"
if(d==2){mycolname<-"Day2_RDT_logRT_LI"}
polarity <- (1)
allsum <- makeLI(allsum,origdat,task,mycolname,polarity,mycutoff)
}
# plot log RT
cor1<-cor(allsum$Day1_RDT_logRT_LI,allsum$Day2_RDT_logRT_LI,use='complete.obs')
plot(allsum$Day1_RDT_logRT_LI,allsum$Day2_RDT_logRT_LI,main='Rhyme detect: LI for log RT')
abline(v=0)
abline(h=0)
text(-1,1,paste0('r = ',round(cor1,3)))
# FINALLY, make t-test for logRT
#remove 'no rhyme' trials
for (d in 1:2){
  thisdat<-RDT_logdat2[RDT_logdat2$side %in% c('left','right'),]
  if(d==1){
    thisdat<-RDT_logdat1[RDT_logdat1$side %in% c('left','right'),]
  }

# add t score to the data
t_dat <- select(pairedt, -3, -5)
t_dat <- na.omit(t_dat)
# relabel for merging
names(t_dat)[names(t_dat) == "t1"] <- "logt1"
names(t_dat)[names(t_dat) == "t2"] <- "logt2"
# merge to allsum for analysis
allsum <- merge(allsum, t_dat, by.x = "origID", by.y = "subject", all.x=T)

Even when log-transforming, things don't look any better.

@@

if(d==1){all_finger1 <- finger}
}

# lets keep a running check on the participants completing here
complete.day2.FT <- unique(all_finger2$subject)
```

@@

### list of participants who completed.

We need a list of participants here who completed the both days for later filtering.

````{r lister}
# CF
day2.CF <- data.frame(matrix(nrow=length(complete.day2.CF), ncol= 2))
  colnames(day2.CF) <- c("task", "subject")
  day2.CF$subject <- complete.day2.CF
  day2.CF$task <- "CF"
# DL
day2.DL <- data.frame(matrix(nrow=length(complete.day2.DL), ncol= 2))
  colnames(day2.DL) <- c("task", "subject")
  day2.DL$subject <- complete.day2.DL
  day2.DL$task <- "DL"
# RD
day2.RD <- data.frame(matrix(nrow=length(complete.day2.RD), ncol= 2))
  colnames(day2.RD) <- c("task", "subject")
  day2.RD$subject <- complete.day2.RD
  day2.RD$task <- "CF"
# Finger
day2.FT <- data.frame(matrix(nrow=length(complete.day2.FT), ncol= 2))
  colnames(day2.FT) <- c("task", "subject")
  day2.FT$subject <- complete.day2.FT
  day2.FT$task <- "CF"
# now create a combined df
complete.day2a <- merge(day2.CF, day2.DL, by= "subject")
complete.day2b <- merge(day2.RD, day2.FT, by= "subject")
complete.day2 <- merge(complete.day2a, complete.day2b, by= "subject")
# add row to code
complete.day2$day2.complete <- 1
complete.day2 <- select(complete.day2, -2, -3, -4, -5)
# now merge into allsum
allsum <- merge(allsum, complete.day2, by= "subject", all= TRUE)

# now write this for filtering
write.csv(allsum, "LIs.csv")
```

### data frames for general plots

In the MS we add a section on raw scores (simple plots). To do this, we require a data frame for each measure.

```{r dataMS}
# DAY 1
# add task ID
chim_dat1$task <- "CF"
DL_dat1$task <- "DL"
RDT_df1$task <- "RD"
# merge and add day
plot_data_1 <- rbind(chim_dat1, DL_dat1, RDT_df1[RDT_df1$side != "no rhyme",])
  plot_data_1$Session<- 1

# DAY 2
chim_dat2$task <- "CF"
DL_dat2$task <- "DL"
RDT_df2$task <- "RD"
# merge and add day
plot_data_2 <- rbind(chim_dat2, DL_dat2, RDT_df2[RDT_df2$side != "no rhyme",])
  plot_data_2$Session<- 2

# merge both
plot.data <- rbind(plot_data_2, plot_data_1)

# remove those who only did day 1
plot.data <- merge(plot.data, complete.day2, by= "subject")

# make look up for lextale and remove
lexLOOK <- allsum %>% dplyr::select("subject", "lexTALE")
lexLOOK <- lexLOOK[lexLOOK$lexTALE >= 80,]
# remove those wuth poor lextale
plot.data <- merge(plot.data, lexLOOK, by= "subject")

# now look up exclusions 
excludeLOOK <- allsum %>% dplyr::select("subject", "exclude", "exRDT")
plot.data <- merge(plot.data, excludeLOOK, by= "subject")

# make style conistent
plot.data$side <- tolower(plot.data$side)

# save data frame
write.csv(plot.data, "./data/for_figs.csv")
```

### Reduce to .75

In our pre-registration, we specified that we would reduce the number of trials required for tasks yielding greater than .75 test-retest relaibility until w have a reliability of .65. However, given that this is actually considerably lovwer than the results obtained. We instead decided to do this until the reliability was .75. When removing outliers and exlcuding, we achieve this for the dichotic listening and chimeric faces. The code below reduces the data frame and then creates LIs.

#### Chimeric faces

```{r reducer}
{for (d in 1:2){ #we will process day 1 and day 2 together
  dat <- CF_dat1
  if (d==2)
  {dat <- CF_dat2}

trial <- 96
nsub <-(unique(dat$subject))

myrow <- 0 # start row counter
temp.dat <- data.frame(matrix(ncol = 4, nrow=length(nsub)*2*trial))
  colnames(temp.dat) <- c("subject", "side", "accurate", "trial")
for (z in nsub) {

    subname <- z
    myrows <- which(dat$subject==subname) # select rows for this subject
    tmp <- dat[myrows,]

    # loop through subjects
    for (y in 1:trial) {
      # limit data here
      tmp2 <- tmp[1:y,]
      tmp2 <- tmp2[tmp2$side != "X",]
      tmp2 <- tmp2 %>% mutate(side= if_else(side== "Left", 1, 2))

      for (s in 1:2) {

        tmp3 <- tmp2[tmp2$side== s,]

        myrow <- myrow+1
        temp.dat$subject[myrow] <- z
        temp.dat$accurate[myrow] <- sum(tmp3$Correct,na.rm=TRUE) # add row for N accurate response
        temp.dat$trial[myrow] <- y
        temp.dat$side[myrow] <- if_else(s== 1, "Left", "Right")
      }
    }
  }
  chim.iter2<- temp.dat
  if (d==1)
  {chim.iter <- chim.iter2}
}
# now remove NAs to avoid any issues later
chim.iter <- na.omit(chim.iter)
chim.iter2 <- na.omit(chim.iter2)
# create another data frame
myrow.2 <- 0 # start row counter
CF.corrs <- data.frame(matrix(ncol = 2, nrow=200))
  colnames(CF.corrs) <- c("trial", "cor")
# LOOP THROUGH TRIAL SIZE
for (y in 2:trial) {
# task
task<-'Chimeric faces'  
# now identify the data frame
origdat <- chim.iter[chim.iter$trial== y,]
origdat$X1 <- origdat$accurate
mycolname<-"Day1_CF_moving"
mycutoff <- 0
polarity<- (-1)#so LI is positive in predicted direction
# select df
newsum <- dplyr::select(allsum, subject, exclude, lexTALE)
# make LIs for day 1
move <- makeLI(newsum,origdat,task,mycolname,polarity,mycutoff)
# make LIs for day 2
origdat2 <- chim.iter2[chim.iter2$trial== y,]
origdat2$X1 <- origdat2$accurate
mycolname<-"Day2_CF_moving"
move <- makeLI(move,origdat2,task,mycolname,polarity,mycutoff)
move <- move[move$exclude == 0 | move$exclude == 2,]
# correlate
move_corr <- cor(move[move$lexTALE <= 80,]$Day1_CF_moving, move[move$lexTALE <= 80,]$Day2_CF_moving, use= "complete.obs")

  # write to data 
  myrow.2 <- myrow.2+1
  CF.corrs$trial[myrow.2] <- y
  CF.corrs$cor[myrow.2] <- move_corr
}
# plot
CF.corrs <- na.omit(CF.corrs)
CF.cor.plot <- ggplot(CF.corrs, aes(x=trial, y=cor)) +
  geom_hline(yintercept=.65, linetype="dashed", color = "blue") +
  geom_hline(yintercept=.75, linetype="dashed", color = "red") +
  geom_line(size=1, alpha=0.8) + ylim(0, 1) + theme_classic() +
  xlab("No. of trials") + ylab("Test-retest reliability") + ggtitle("B") + theme(plot.title = element_text(hjust = 0.5))
# print number of trials needed
print(paste0("Number of chimeric faces required for at least .65 test-retest: ", min(CF.corrs[CF.corrs$cor >= .65,]$trial)))
print(paste0("Number of chimeric faces required for at least .75 test-retest: ", min(CF.corrs[CF.corrs$cor >= .75,]$trial)))
}
```

Based on a couple of rounds with this, removing a lower limit on trials correct here is the only way to examine if less than 1 block would be enough to achieve r= .75. From this analysis, it appears that 27 trials would be sufficient to run the chimeric faces wirth reasonable reliability. Three repetitions of all combinations would lead to 48 trials (36 with different emotions in each hemifield, 12 same-same trials). This would ensure full balancing as 27 items would not allow an equal presentation of each of the four emotions across hemifaces.

#### Dichotic listening

```{r reducerDL}
{for (d in 1:2){ #we will process day 1 and day 2 together
  dat <- dichotic_dat1
  if (d==2)
  {dat <- dichotic_dat2}

# format for conistency    
dat <- 
  dat %>% 
  mutate(side= ifelse(as.character(Response) == as.character(left_channel) & Correct == 1, "Left",
                       ifelse(as.character(Response) == as.character(right_channel) & Correct == 1, "Right", "X")))
# code side as factor

trial <- 120
nsub <-(unique(dat$subject))
